% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration
%
\begin{document}
\mainmatter              % start of the contributions
%
\title{Exploratory Analysis of Text Collections Using Parallel Hierarchical Clustering}
%
\titlerunning{Parallel HC}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Haimonti Dutta\inst{1} \and Mihir Chauhan\inst{2}
Akshat Sehgal\inst{1} }
%
\authorrunning{Dutta et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{Department of Management Science and Systems (MSS), University at Buffalo, NY 14250, USA,\\
\email{haimonti@buffalo.edu},\\ WWW home page:
\texttt{www.buffalo.edu/~haimonti}
\and
Department of Computer Science,
University at Buffalo, NY 14250, USA\\
}

\maketitle              % typeset the title of the contribution

\begin{abstract}
Write Something
 \dots
\keywords{computational geometry, graph theory, Hamilton cycles}
\end{abstract}
%
\section{Introduction}
%
%
\section{Tool Overview}

\subsection{Architecture}
\subsection{Parallel HC}
\subsection{Coresets}

\subsection{Case Study}

\noindent 
 %
% ---- Bibliography ----
%
\begin{thebibliography}{5}
%
\bibitem {clar:eke}
Clarke, F., Ekeland, I.:
Nonlinear oscillations and
boundary-value problems for Hamiltonian systems.
Arch. Rat. Mech. Anal. 78, 315--333 (1982)

\bibitem {clar:eke:2}
Clarke, F., Ekeland, I.:
Solutions p\'{e}riodiques, du
p\'{e}riode donn\'{e}e, des \'{e}quations hamiltoniennes.
Note CRAS Paris 287, 1013--1015 (1978)

\bibitem {mich:tar}
Michalek, R., Tarantello, G.:
Subharmonic solutions with prescribed minimal
period for nonautonomous Hamiltonian systems.
J. Diff. Eq. 72, 28--55 (1988)

\bibitem {tar}
Tarantello, G.:
Subharmonic solutions for Hamiltonian
systems via a $\bbbz_{p}$ pseudoindex theory.
Annali di Matematica Pura (to appear)

\bibitem {rab}
Rabinowitz, P.:
On subharmonic solutions of a Hamiltonian system.
Comm. Pure Appl. Math. 33, 609--633 (1980)

\end{thebibliography}


\clearpage
\addtocmark[2]{Author Index} % additional numbered TOC entry
\renewcommand{\indexname}{Author Index}
\printindex

\end{document}
